---
title: "NE PVA Parameter log"
output: 
   word_document:
     reference_docx: "NEPVA-styles.docx"
params: 
  d: NA
  ui_ver: NA
  pva_ver: NA
---

# Set up 
The log file was created on: `r params$d`  

R version `r getRversion()`, NEPVA package version: `r pva_ver` (with UI version `r ui_ver`)

```{r Package information, echo=FALSE}
packinfo <- installed.packages(fields = c("Package", "Version"))
packinfo[c("popbio","shiny","shinyjs","shinydashboard","shinyWidgets","DT","plotly","rmarkdown","dplyr","tidyr"),c("Package", "Version")]
```

# Basic information
This run had reference name `r input$runrefname`.  
PVA model run type: `r input$run_type`.      
Model to use for environmental stochasticity: `r input$model_envstoch`.    
Model for density dependence: `r input$model_dd`.    
Include demographic stochasticity in model?: `r ifelse(input$model_demostoch,"Yes","No")`.   
Number of simulations: `r input$sim_n`.      
Random seed: `r input$sim_seed`.    
Case study selected: `r input$case_studies`.  

# Baseline demographic rates
Species chosen to set initial values: `r input$species`.    
Region type to use for breeding success data: `r input$poolregtypeBS`.   
Sector to use within breeding success region: `r input$poolregionBS`.  
Age at first breeding: `r input$afb`.    
Is there an upper constraint on productivity in the model?: `r ifelse(input$model_prodmax,paste0("Yes, constrained to ",input$mbs," per pair"),"No")`.      
Number of subpopulations: `r input$npop`.    
Format for initial population size: `r input$inipop_inputformat`  
Are demographic rates applied separately to each subpopulation?: `r ifelse(input$demobase_splitpops,"Yes","No")`.    
Are baseline demographic rates specified separately for immatures?: `r ifelse(input$demobase_splitimmat,"Yes","No")`.    

```{r demobase, echo=FALSE, results="asis"}
for (i in 1:input$npop) {
   cat("### Population ",i,"  \n")
   cat("**Initial population values:** \n")
   cat("Initial population ", input[[paste0("inipopval_",i)]], " in ", input[[paste0("inipopyrs_",i)]],"\n\n")
   cat("**Productivity rates:** \n")
   if (input$model_dd == "nodd") {
   cat("mean: ",input[[paste0("pr_mn_",i)]],", sd: ", input[[paste0("pr_sd_",i)]], "\n\n")
   cat("**Adult survival rates:** \n")
   cat("mean: ",input[[paste0("ad_mn_",i)]],", sd: ", input[[paste0("ad_sd_",i)]], "\n\n")
   } else {
   cat("mean: ",input[[paste0("pr_mn_",i)]],", sd: ", input[[paste0("pr_sd_",i)]], ", DD:", input[[paste0("pr_idd_",i)]],"\n\n")
   cat("**Adult survival rates:** \n")
   cat("mean: ",input[[paste0("ad_mn_",i)]],", sd: ", input[[paste0("ad_sd_",i)]], ", DD:", input[[paste0("ad_idd_",i)]],"\n\n")
   }
   if (input$demobase_splitimmat){
      cat("**Immatures survival rates:** \n\n")
      for (j in 1:input$afb) {
         cat("Age class ",j-1," to ",j," - ")
         cat("mean: ",input[[paste0("im_mn_",i,"_",j)]],
            ", sd: ", input[[paste0("im_sd_",i,"_",j)]], 
            ", DD: ", input[[paste0("im_idd_",i,"_",j)]],"\n\n")
      }
      cat("\n")}
}
```

# Impacts
Number of impact scenarios: `r input$nscen`.    

```{r impact, eval={input$nscen>0}, echo=FALSE, results="asis"}
cat("Are impacts applied separately to each subpopulation?: ", ifelse(input$impacts_splitpops,"Yes","No"),"\n\n")   
cat("Are impacts of scenarios specified separately for immatures?: ", ifelse(input$impacts_splitimmat,"Yes","No"),"\n\n")    
cat("Are standard errors of impacts available?: ", ifelse(input$impacts_provideses,"Yes","No"),"\n\n")    
cat("Should random seeds be matched for impact scenarios?: ", ifelse(input$impacts_matchscens,"Yes","No"),"\n\n")    
cat("Are impacts specified as a relative value or absolute harvest?: ", input$impacts_relative,"\n\n")    
cat("Years in which impacts are assumed to begin and end: ", input$impacts_year[1], " to ", input$impacts_year[2],"\n\n")   

cat("## Impact on Demographic Rates","\n\n")
 for (s in 1:input$nscen) {
   cat("### Scenario ",LETTERS[s]," - Name: ",input[[paste0("scn_nm_str_",s)]],"\n\n")
   ifelse (input$impacts_splitpops, np <- input$npop, np <- 1)
   for (i in 1:np) {
      if (input$impacts_splitpops) {
         cat("#### Population ",i,"  \n")
      } else {
         cat("#### All subpopulations \n") 
      } 
      if (input$impacts_relative == "relative") {
         cat("**Impact on productivity rate **")
      } else {
         cat("**Number of chicks harvested **")
      }
      cat("mean: ",input[[paste0("imp_pr_mn_",s,"_",i)]],", se: ", input[[paste0("imp_pr_se_",s,"_",i)]],"\n\n")
      if (input$impacts_relative == "relative") {
         cat("**Impact on adult survival rate **")
      } else {
         cat("**Number of adults harvested **")
      }
      cat("mean: ",input[[paste0("imp_ad_mn_",s,"_",i)]],", se: ", input[[paste0("imp_ad_se_",s,"_",i)]],"\n\n")
      if (input$impacts_splitimmat) {
         if (input$impacts_relative == "relative") {
            cat("**Impact on immature survival rate **")
         } else {
            cat("**Number of immatures harvested **")
         }
         cat("mean: ",input[[paste0("imp_im_mn_",s,"_",i)]],", se: ", input[[paste0("imp_im_se_",s,"_",i)]],"\n\n")
      }
      cat("\n")
   }
}
```

## Output:
```{r outputyear, echo=FALSE, results="asis"}
output_yr_end <- input$output_year_end
if (input$nscen > 0 & (input$output_year_end < input$impacts_year[1] + 1)) {
   output_yr_end <- input$impacts_year[1] + 1
}
output_yr_start <- input$output_year_start
if (input$run_type == 'simplescenarios' & !is.na(output_yr_start)) {
   if (output_yr_start >= output_yr_end) {
      output_yr_start <- max(minyr, output_yr_end - 1)
   }
}

```
First year to include in outputs: `r output_yr_start`    
Final year to include in outputs: `r output_yr_end`    
How should outputs be produced, in terms of ages?: `r input$output_agetype`    
Target population size to use in calculating impact metrics: `r input$output_popsize_target`    
Quasi-extinction threshold to use in calculating impact metrics: `r input$output_popsize_qe`    

```{r Sensitivity-only, eval={input$run_type=="sensitivity.local"}, echo=FALSE, results="asis"}
cat("## Sensitivity parameters","\n")
cat("**sens_npvlocal** = ", input$sens_npvlocal,"\n\n")
cat("**sens_pcr** = c(", input$sens_pcr_1,", ",input$sens_pcr_2,", ",input$sens_pcr_3,", ",input$sens_pcr_4,", ",input$sens_pcr_5,")")
```


```{r validation-only, eval={input$run_type=="validation"}, echo=FALSE, results="asis"}
cat("## Validation data","\n")
for (i in 1:20) {
   if (!is.na(input[[paste0("output_validation_years_",i)]])){
      cat(input[[paste0("output_validation_counts_",i)]]," in ",input[[paste0("output_validation_years_",i)]],"\n\n")
   } 
}
```

